How to use flowCore package

### 2007-01-22 inst/doc/HowTo-flowCore.Rnw
* Converted multipleFilterResult to use factors rather than keeping the two separate. This makes more sense vis a vis %in% operators and makes the initialization of the multipleFilterResult object unnecessary.
* Added the ability to %subset% a multipleFilterResult such a way that the subsetting filter is applied to each population to construct a narrower population.

git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@21517 bc3139a8-67e5-0310-9ffc-ced21a209358
fix vignette remains documentation error with check
git-svn-id: file:///home/git/hedgehog.fhcrc.o

<<define and apply rangeGate1,eval=TRUE, echo=FALSE,results=hide>>=
rangeGate <- rectangleGate(filterId="rangeGate","FSC-H"=c(.2,Inf))
b08rangeGate <- filter(b08,rangeGate)
@ 
<<plotfiltered, eval=TRUE, echo=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08rangeGate, pch="*",main="B08, lower debris")
@ 
<<define and apply ploygoneGate2,eval=TRUE, echo=FALSE,results=hide>>=
rectGate <- rectangleGate(filterId="nonDebris","FSC-H"=c(0.2,0.8),"SSC-H"=c(0,0.8))
b08rectGate <- filter(b08,rectGate)
b08Filtered <- b08[b08rectGate,]
@ 
<<plotCenterfiltered, eval=TRUE, echo=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08rectGate,pch="*",main="B08 - Nondebris")
@

\begin{figure}
\centering
\subfigure{\includegraphics[width=40mm]{plotfiltered} A}
\subfigure{\includegraphics[width=40mm]{plotCenterfiltered} B} 
\caption{
  \label{fig:Fig02}{Example of the effect of filtering with a rectangular gate.}} 
\end{figure}

@@

<<plotRectanglefilter, eval=TRUE, echo=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=b08sqrfilter,pch="*")
@

<<define and apply polygonGate,eval=TRUE,echo=FALSE>>=
triangleCut <- matrix(c(0.3,0.4,0.6,0.3,0.4,0.3),ncol=2,nrow=3)
colnames(triangleCut) <- c("FSC-H","SSC-H")
trianglefilter <- polygonGate(filterId="nonDebris",boundaries= triangleCut)
b08Trgfilter <- filter(b08,trianglefilter)
@

<<plotTrianglefilter, eval=TRUE, echo=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(x=b08,y=b08Trgfilter,filter=trianglefilter,colSubSet="red",pch="*")
@

\begin{figure}
\centering
\subfigure{\includegraphics[width=40mm]{plotRectanglefilter} A}
\subfigure{\includegraphics[width=40mm]{plotTrianglefilter} B} 
\caption{
  \label{fig:Fig03}{Example of the effect of filtering with a
    polygon gate.}} 
\end{figure}

>>>>

<<define and apply rangeGate1,eval=TRUE, echo=FALSE,results=hide>>=
rangeGate <- rectangleGate(filterId="rangeGate","FSC-H"=c(.2,Inf))
b08rangeGate <- filter(b08,rangeGate)
@ 
<<plotTOfilter, eval=TRUE, echo=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y="FSC-H", pch="*",main="B08, with debris")
@
<<plotfiltered, eval=TRUE, echo=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08[b08rangeGate],y="FSC-H", pch="*",main="B08, lower debris removed")
@

\begin{figure}
\centering
\subfigure{\includegraphics[width=40mm]{plotTOfilter} A}
\subfigure{\includegraphics[width=40mm]{plotCenterfiltered} B} 
\caption{
  \label{fig:Fig02}{Example of the effect of filtering out low intensities debris with a rectangular gate.}} 
\end{figure}

<<define and apply ploygoneGate2,eval=TRUE, echo=FALSE,results=hide>>=
rectGate <- rectangleGate(filterId="nonDebris","FSC-H"=c(0.2,0.8),"SSC-H"=c(0,0.8))
b08rectGate <- filter(b08,rectGate)
b08Filtered <- b08[b08rectGate,]
@ 
<<plot3, eval=TRUE, echo=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08,y=c("FL1-H","FL2-H"),pch="*",main="B08 - Nondebris")
@
<<plot4, eval=TRUE, echo=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08Filtered,y=c("FL1-H","FL2-H"),pch="*",main="B08 - Nondebris")
@

\begin{figure}
\centering
\subfigure{\includegraphics[width=40mm]{plot3} A}
\subfigure{\includegraphics[width=40mm]{plot4} B} 
\caption{
  \label{fig:Fig03}{Second example of the effect of filtering out low intensities debris with a rectangular gate.}} 
\end{figure}

@@

<<plotRectanglefilter, eval=TRUE, echo=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(b08[b08sqrfilter],pch="*")
@

<<define and apply polygonGate,eval=FALSE,echo=FALSE>>=
triangleCut <- matrix(c(0.3,0.4,0.6,0.3,0.4,0.3),ncol=2,nrow=3)
colnames(triangleCut) <- c("FSC-H","SSC-H")
trianglefilter <- polygonGate(filterId="nonDebris",boundaries= triangleCut)
b08Trgfilter <- filter(b08,trianglefilter)
@

<<plotTrianglefilter, eval=FALSE, echo=FALSE, fig=TRUE, prefix=FALSE, include=FALSE>>=
plot(x=b08,y=b08Trgfilter,filter=trianglefilter,colSubSet="red",pch="*")
@

%%\begin{figure}
%%\\centering
%%\\subfigure{\includegraphics[width=40mm]{plotRectanglefilter} A}
%%\\subfigure{\includegraphics[width=40mm]{plotTrianglefilter} B} 
%%\\caption{
%%\  \label{fig:Fig03}{Example of the effect of filtering with a
%%\    polygon gate.}} 
%%\\end{figure}
